---
output: github_document
---

[![Travis build status](https://travis-ci.org/ATFutures/ical.svg?branch=master)](https://travis-ci.org/ATFutures/ical)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ical

The goal of ical is to work with iCalander (`.ics`, `.ical` or similar) files in R.
iCalendar is an open standard for
"exchanging calendar and scheduling information between users and computers"
described at [icalendar.org](https://icalendar.org/) (the full spec can be found in a 
plain text file [here](https://tools.ietf.org/rfc/rfc5545.txt)).

Recently the UK Government endorsed the iCal format in a [publication](https://www.gov.uk/government/publications/open-standards-for-government/exchange-of-calendar-events) Open Standards for Government' series.
[An example .ics file](https://www.gov.uk/bank-holidays/england-and-wales.ics) is provided by the .gov.uk domain, which shows holidays in England and Wales.

## Installation

```{r, eval=FALSE}
devtools::install_github("ATFutures/ical")
```

```{r}
library(ical)
```

<!-- You can install the released version of ical from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("ical") -->
<!-- ``` -->

## Example

A minimal example representing the contents of an iCalendar file is provided in the dataset `ic_example`, which is loaded when the package is attached.
This is what iCal files look like:

```{r min-example}
ic_example
```

Relevant fields can be found and extracted as follows:

```{r}
ic_find(ic_example, "TSTAMP")
ic_extract(ic_example, "TSTAMP")
```

A larger example shows all national holidays in England and Wales.
It can be read-in as follows:

```{r example}
ics_file <- system.file("extdata", "england-and-wales.ics", package = "ical")
ics_raw = readLines(ics_file) 
head(ics_raw) # check it's in the ICS format
```

A list representation of the calendar can be created using `ic_list()` as follows:

```{r}
ics_list = ic_list(ics_raw, pattern = "VEV")
ics_list[1:2]
```

A data frame representing the calendar can be created as follows (work in progress, not yet working):

```{r}
ics_df = ic_read(ics_file) # read it in
head(ics_df) # check the results
```

What class is each column?

```{r cars}
vapply(ics_df, class, character(1))
```


## Related projects

- A Python package for working with ics files: https://github.com/C4ptainCrunch/ics.py
