---
output: github_document
---
[![](http://www.r-pkg.org/badges/version/calendar)](https://www.r-pkg.org:443/pkg/calendar)
[![The API of a maturing package has been roughed out, but finer details likely to change.](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Travis build status](https://travis-ci.org/ATFutures/calendar.svg?branch=master)](https://travis-ci.org/ATFutures/calendar)
[![Coverage status](https://codecov.io/gh/ATFutures/calendar/branch/master/graph/badge.svg)](https://codecov.io/github/ATFutures/calendar?branch=master)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# calendar

The goal of calendar is to make it easy to create, read, write, and work with iCalander (`.ics`, `.ical` or similar) files, and the scheduling data they represent, in R.
iCalendar is an open standard for
"exchanging calendar and scheduling information between users and computers"
described at [icalendar.org](https://icalendar.org/) (the full spec can be found in a 
plain text file [here](https://tools.ietf.org/rfc/rfc5545.txt)).

Recently the UK Government endorsed the iCal format in a [publication](https://www.gov.uk/government/publications/open-standards-for-government/exchange-of-calendar-events) for the 'Open Standards for Government' series.
[An example .ics file](https://www.gov.uk/bank-holidays/england-and-wales.ics) is provided by the .gov.uk domain, which shows holidays in England and Wales.

## Installation
```{r install-cran, eval=FALSE}
install.packages("calendar")
```

Or install the cutting edge from GitHub
```{r, message=FALSE, results='hide'}
devtools::install_github("ATFutures/calendar")
```

```{r}
library(calendar)
```

<!-- You can install the released version of calendar from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("calendar") -->
<!-- ``` -->

## Example

A minimal example representing the contents of an iCalendar file is provided in the dataset `ical_example`, which is loaded when the package is attached.
This is what iCal files look like:

```{r min-example}
ical_example
```

Relevant fields can be found and extracted as follows:

```{r}
which(ic_find(ical_example, "TSTAMP"))
ic_extract(ical_example, "TSTAMP")
```

A larger example shows all national holidays in England and Wales.
It can be read-in as follows:

```{r example}
ics_file <- system.file("extdata", "england-and-wales.ics", package = "calendar")
ics_raw = readLines(ics_file) 
head(ics_raw) # check it's in the ICS format
```

A list representation of the calendar can be created using `ic_list()` as follows:

```{r}
ics_list = ic_list(ics_raw)
ics_list[1:2]
```

A data frame representing the calendar can be created as follows (work in progress):

```{r}
ics_df = ic_read(ics_file) # read it in
head(ics_df) # check the results
```

What class is each column?

```{r cars}
vapply(ics_df, class, character(1))
```

## Trying on calendars 'in the wild'

To make the package robust we test on a wide range of ical formats.
Here's an example from my work calendar, for example:

```{r}
my_cal = ic_dataframe(ical_outlook)
my_cal$SUMMARY[1]
# calculate the duration of the European R users meeting event:
my_cal$`DTEND;VALUE=DATE`[1] - my_cal$`DTSTART;VALUE=DATE`[1]
```

<!-- An example from the wild: -->

```{r, echo=FALSE, eval=FALSE}
my_cal = ic_read("https://outlook.office365.com/owa/calendar/63f6c4e85d124df6a20656ade8e71faa@leeds.ac.uk/32e1cb4137f4414b8d7644453ec4b10414316826143036893453/calendar.ics")

attributes(my_cal)$ical
# head(my_cal[c("DESCRIPTION", "SUMMARY", "DTSTART", "DTEND", "STATUS", "SEQUENCE", "LOCATION")])
```

## Related projects

- A Python package for working with ics files: https://github.com/ics-py/ics-py
- A JavaScript package by Mozilla: https://github.com/mozilla-comm/ical.js/
- Ruby library: https://github.com/icalendar/icalendar
- The ical R package on CRAN for reading .ics files: https://github.com/petermeissner/ical
