---
title: "Creating calendars with ical and R"
author: "Robin Lovelace"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**ical** allows you to read-in 'ical files' (which typically have the `.ics` filetype) with `ic_read()`.
However, often it's useful to create your own `ical` object from scratch.
The purpose of this vignette is to show how, with reference to a real-world application: creating a timetable for a new module.

It assumes you've installed the package following instructions in the [README](https://github.com/ATFutures/ical#installation) and have attached it as follows:

```{r}
library(ical)
```


## Creating events

The building blocks of most calendars the event.
All events have a start point and an end point (unless they are an all day event) and a summary description.
As shown in the example below, they also tend to contain other fields.

```{r}
# key:value pairs in an ical example:
ic_list(ical_example)[[1]]
```

Fortunately you don't need to specify all of these when creating events because some will be created manually and some are not necessary.
Events can be created as follows:

```{r}
s = as.POSIXct("2018-09-27 13:00")
event = ic_event(start = s, end = s + 60^2, summary = "Minihackathon!")
event
class(event)
ic_character(event)
```


