---
title: "Creating calendars with ical and R"
author: "Robin Lovelace"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**ical** allows you to read-in 'ical files' (which typically have the `.ics` filetype) with `ic_read()`.
However, often it's useful to create your own `ical` object from scratch.
The purpose of this vignette is to show how, with reference to a real-world application: creating a timetable for a new module.

It assumes you've installed the package following instructions in the [README](https://github.com/ATFutures/ical#installation) and have attached it as follows:

```{r}
library(ical)
```


## Creating events

The building blocks of most calendars the event.
All events have a start point and an end point (unless they are an all day event) and a summary description.
As shown in the example below, they also tend to contain other fields.
Fortunately you don't need to specify all of these when creating events because some will be created manually and some are not necessary.

```{r}
ic_list(ical_example)
```

